Gap formation and stability in non-isothermal protoplanetary discs

### 2015-02-06 paper/results.tex
Minor addition to referees comments

\subsection{Axisymmetric stability}
The initial planet-disc interaction form bumps and grooves in the gap profiles
which can potentially be unstable due to axisymmetric instabilities. The
generalised local axisymmetric stability condition is the Solberg-Hoiland
criterion,  
\begin{align}
  \kappa^2+N^2 \geq 0 
\end{align}
where
\begin{align}
 N^2=\frac{1}{\Sigma} \frac{\partial P}{\partial r}
 \left(\frac{1}{\Sigma} \frac{\partial \Sigma}{\partial
     r}-\frac{1}{\gamma P} \frac{\partial P}{\partial r}  \right) 
\end{align}
is the square of the Brunt-V\"ais\"al\"a frequency. 
At the outer gap edge $r=r_p+2.5r_h$,  where the RWI is excited
(see below), we find $\kappa^2 + N^2$ reaches local minimum with a value
$\sim 2\times10^{-4}$ (code units) for all $\tilde\beta$. The
Brunt-V\"ais\"al\"a frequency is $N\sim 10^{-5}$, decreasing marginally with longer cooling rate. 
The Solberg-Hoiland criteria is similarly satisfied for the entire 2D disc throughout the 
simulations.
Thus for all values of $\tilde\beta$ the planet-induced gaps are
stable to axisymmertic instabilities.

@@

Table \ref{modetable} show that as
$\tilde{\beta}$ is increased from $ 0.1\rightarrow10$ the dominant
azimuthal Fourier mode decreases from $ m=9\rightarrow3$ and the
respective growth rate decreases from $ \gamma/\Omega(r_p)=0.079
\rightarrow 0.017$. However, despite two orders of magnitude increase in the
cooling time, the instability remains dynamical with characteristic  growth time
$\lesssim 10P_0$. Snapshots of the instability in for  
the different $\tilde\beta$ are shown in Fig \ref{2Dlinear}.

@@

\begin{figure}
  \includegraphics[width=\linewidth,height=\linewidth]{figures/vortex2D}
  \caption{Relative surface density perturbation for the
    $\tilde\beta=0.1$ case during quasi-steady state with a single
    vortex at the outer gap edge. 
    The plots for other values of the cooling time
    $\tilde{\beta}$ are similar.
    \label{Vortex2D}} 
\end{figure}

@@

>>>>

\subsection{Axisymmetric stability}
The initial planet-disc interaction form bumps and grooves in the gap profiles
which can potentially be unstable due to axisymmetric instabilities. The
generalised local axisymmetric stability condition is the Solberg-Hoiland
criterion,  
\begin{align}
  \kappa^2+N^2 \geq 0 
\end{align}
where
\begin{align}
 N^2=\frac{1}{\Sigma} \frac{\partial P}{\partial r}
 \left(\frac{1}{\Sigma} \frac{\partial \Sigma}{\partial
     r}-\frac{1}{\gamma P} \frac{\partial P}{\partial r}  \right) 
\end{align}
is the square of the Brunt-V\"ais\"al\"a frequency. 
At the outer gap edge $r=r_p+2.5r_h$,  where the RWI is excited
(see below),{\bf  we find $\kappa^2 + N^2$ reaches local minimum with a value
$\sim 0.45 \, \Omega^2(r_p)$
%$\sim 2\times10^{-4}$ (code units)
 for all $\tilde\beta$. The
Brunt-V\"ais\"al\"a frequency at the outer gap edge is
$N\sim 10^{-2} \, \Omega^2(r_p)$,}
% $N\sim 10^{-5}$,
decreasing marginally with longer cooling rate. 
The Solberg-Hoiland criteria is similarly satisfied for the entire 2D disc throughout the 
simulations.
Thus for all values of $\tilde\beta$ the planet-induced gaps are
stable to axisymmertic instabilities.

@@

Table \ref{modetable} show that as
$\tilde{\beta}$ is increased from $ 0.1\rightarrow10$ the dominant
azimuthal Fourier mode decreases from $ m=9\rightarrow3$ and the
respective growth rate decreases from $ \gamma/\Omega(r_p)=0.079
\rightarrow 0.017$. However, despite two orders of magnitude increase in the
cooling time, the instability remains dynamical with characteristic  growth time
$\lesssim 10P_0$. Snapshots of the instability in for  
the different $\tilde\beta$ are shown in Fig \ref{2Dlinear}. {\bf Isothermal simulations with set sound speed where also analyzed showing growth rates $\sim 5 \times 10^2 / \Omega(r_p)$. In comparison nearly isothermal simulation with $\tilde\beta=0.01$ had growth rates $\sim 8\times 10^2 / \Omega(r_p)$}

@@

\begin{figure}
  \includegraphics[width=\linewidth,height=\linewidth]{figures/vortex2D}
  \caption{Relative surface density perturbation for the
    $\tilde\beta=0.1$ case during quasi-steady state with a single
    vortex at the outer gap edge. 
    The plots for other values of the cooling time
    $\tilde{\beta}$ are similar.
    {\bf The decrease in density pertibation at $r>40r_{in}$ arises from the open
    boundry condition.}
    \label{Vortex2D}} 
\end{figure}

@@

{\bf Radial locations of the vortices were found to migrate over their lifetime. During the quasi-steady state the vortices were found to orbit $\sim 6.5r_h$ from the planet radius. Simultaneously with the appearence of wakes, the vortices were found to move towards $\sim 5.3r_h$. This is a result of the the spiral waves transporting angular momentum to the disk (Is this true? Shocks on the inner disk seem stronger so I would think it would migrate outward). After the vortex reaches marginal amplitudes $<1 \Delta\Sigma/\Sigma$ the vortices were found to migrate back out towards $\sim 6.5 r_h$ from the planet location }
